---
title: "Challenge"
params:
    topic: "Write Bioconductor package templates."
    difficulty: "novice"
    leaders:
        value:
            kevinrue: "Kevin Rue"
    tags:
        - "Getting Started"
        - "Writing Packages"
    duration: "1 hour(s)"
---

```{r, include=FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```

`r params$topic`

## Difficulty

`r stringr::str_to_title(params$difficulty)`.

## Challenge leader(s)

```{r, echo=FALSE, results='asis'}
for (github in names(params$leaders)) {
    profile <- sprintf("http://github.com/%s", github)
    cat(sprintf('- %s - <i class="fab fa-github"></i> [%s](%s)\n', params$leaders[[github]], github, profile))
}
```

## Tags

```{r, echo=FALSE, results='asis'}
cat(sprintf("- `%s`\n", params$tags))
```

## Duration

A minimum of `r params$duration` is recommended for this challenge.

## Notes

- Make template package(s) available as a [GitHub template repository](https://docs.github.com/en/github/creating-cloning-and-archiving-repositories/creating-a-template-repository).
- Consider contributing template packages for the following categories:
    + [Software](https://www.bioconductor.org/packages/devel/BiocViews.html#___Software)
    + [Workflow](https://www.bioconductor.org/packages/devel/BiocViews.html#___Workflow)
    + [AnnotationData](https://www.bioconductor.org/packages/devel/BiocViews.html#___AnnotationData)
    + [ExperimentData](https://www.bioconductor.org/packages/devel/BiocViews.html#___ExperimentData)
