---
title: "Challenge: The SingleCellExperiment Gallery"
params:
    topic: "Contribute to the `SingleCellExperiment` Gallery"
    difficulty: "intermediate"
    leaders:
        value:
            LTLA: "Aaron Lun"
            kevinrue: "Kevin Rue"
    tags:
        - "Single cell"
        - "Visualization"
    duration: "1 hour"
---

```{r, include=FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```

# Topic

`r params$topic`

## Difficulty

`r stringr::str_to_title(params$difficulty)`.

## Challenge leader(s)

```{r, echo=FALSE, results='asis'}
for (github in names(params$leaders)) {
    profile <- sprintf("http://github.com/%s", github)
    cat(sprintf('- %s - <i class="fab fa-github"></i> [%s](%s)\n', params$leaders[[github]], github, profile))
}
```

## Tags

```{r, echo=FALSE, results='asis'}
cat(sprintf("- `%s`\n", params$tags))
```

## Duration

A minimum of `r params$duration` is recommended for this challenge.

## Notes

- Fork the [original repository](https://github.com/LTLA/SCEGallery), working on a branch of your fork, and submitting a pull request when your contribution is ready for review.
- You may contribute new R markdown files or edit existing ones.
- When contributing a new chapter, we recommend reading an [existing chapter](https://github.com/LTLA/SCEGallery/blob/master/reduced-dimensions.Rmd), and using it as a template for your own contribution.
  Contributions written in a style that matches current contents are more likely to be accepted, and more rapidly.
